$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-01-27 paper/e6ssm-tuning-paper.tex
typo fixed
Made some minor changes to the paper

V_{E_6}=V_{E_6}^F+V_{E_6}^D+V_{E_6}^{\textrm{soft}}+\Delta V_{E_6}.

@@

V_{E_6}^F&=\lambda^2|S|^2(|H_1|^2+|H_2|^2)+\lambda^2|(H_1\cdot
H_2)|^2,\label{eq:E6VFterms}\\ V_{E_6}^D&=\frac{\bar{g}^2}{8}\left (

@@

H_2|^2+\frac{g_1'^2}{2}(\tilde{Q}_1|H_1|^2+\tilde{Q}_2|H_2|^2+\tilde{Q}_S|S|^2)^2,\label{eq:E6VDterms}\\ V_{E_6}^{\textrm{soft}}&=m_S^2|S|^2+m_{H_d}^2|H_1|^2+m_{H_u}^2|H_2|^2+\Big

@@

B^\beta=A^2B^1-A^1B^2$. The term $\Delta V_{E_6}$ contains the

@@

of the $U(1)_\chi$ model, $V_{E_6}^F$ may also contain an elementary

@@

  V_{E_6}}{\partial

@@

  \Delta V_{E_6}}{\partial v_2}.

@@

$U(1)_\chi$ models. To satisfy these limits typically requires large

@@

an associated sensitivity coefficient \cite{Feng:2013pwa}

@@

FlexibleSUSY \cite{Athron:2014yba}. The CP-even Higgs masses are

@@

of SOFTSUSY 3.3.10 \cite{Allanach:2001kg,Allanach:2013kza}. For

@@

We have investigated this question here in the context of the MSSM and
U(1) extensions.  Since the RG evolution links the soft masses
together and causes these problems from stop and gluino masses the
most conservative approach to placing naturalness limits is to choose
a low cutoff. We find that in the MSSM the most direct way to
constrain naturalness of the model, without making assumptions about
the SUSY breaking scale is through limits on the chargino
masses. Current LHC limits on charginos are not model independent and
thereby leave many gaps where on can have light charginos.

>>>>

V=V_F+V_D+V_{\textrm{soft}}+\Delta V.

@@

V_F&=\lambda^2|S|^2(|H_1|^2+|H_2|^2)+\lambda^2|(H_1\cdot
H_2)|^2,\label{eq:E6VFterms}\\ V_D&=\frac{\bar{g}^2}{8}\left (

@@

H_2|^2+\frac{g_1'^2}{2}(\tilde{Q}_1|H_1|^2+\tilde{Q}_2|H_2|^2+\tilde{Q}_S|S|^2)^2,\label{eq:E6VDterms}\\ V_{\textrm{soft}}&=m_S^2|S|^2+m_{H_d}^2|H_1|^2+m_{H_u}^2|H_2|^2+\Big

@@

B^\beta=A^2B^1-A^1B^2$. The term $\Delta V$ contains the

@@

of the $U(1)_\chi$ model, $V_F$ may also contain an elementary

@@

  V}{\partial

@@

  \Delta V}{\partial v_2}.

@@

$U(1)_\chi$ models. Bounds on the $Z^\prime$ mass for other $E_6$ inspired models, such as the $U(1)_N$ of the E$_6$SSM, lie between those on the $U(1)_\psi$ and $U(1)_\chi$. To satisfy these limits typically requires large

@@

an associated sensitivity

@@

FlexibleSUSY \cite{Athron:2014yba}, which also makes use of SOFTSUSY \cite{Allanach:2001kg,Allanach:2013kza}. The CP-even Higgs masses are

@@

of SOFTSUSY 3.3.10 \cite{Allanach:2001kg}. For

@@

We have investigated this question here in the context of the MSSM and
U(1) extensions.  Since the RG evolution links the soft masses
together and causes these problems from stop and gluino masses the
most conservative approach to placing naturalness limits is to choose
a low cutoff. We find that in the MSSM the most direct way to
constrain naturalness of the model, without making assumptions about
the SUSY breaking scale is through limits on the chargino
masses. Current LHC limits on charginos are not model independent and
thereby leave many gaps where one can have light charginos.
